AHABus \& FCORE:\\Modular Bus for High-Altitude Balloon Missions

### 2017-04-08 chapters/04-results.tex
Add Aknowledgements
Better table styles

\section{Component Testing}

\section{Integrated Testing}

\subsection{Day In The Life Testing}

@@

\begin{figure}[H]
\begin{tikzpicture}
\begin{axis} [
xlabel=Mission Elapsed Time (\SI{}{\second}),
ylabel=Altitude (\SI{}{\metre}),
mark size=1.0pt,
mark repeat={5},
legend style ={
    at={(0.98,0.95)}, 
    anchor=north east, draw=black, 
    fill=white,align=left
}
]
\addplot+ table [
x=MET, y=altitude, col sep=comma
] {data/test-ditl/loc.csv};
\end{axis}
\end{tikzpicture}
\centering
\caption{DITL Test - Altitude over time}
\label{fig:dit-alt}
\end{figure}

% The mission platform was composed of the AHABus \acrlong{obc}, and two simulated
% payloads: payload 10 at priority level 2, and payload 20 at priority level 1.
% Table \ref{tab:ditl-cfg}.
%
% \begin{table}[H]
% \begin{center}
% \begin{tabular}{ |c|c c c| }
% \hline
% payload & priority & core frequency & polling interval \\
% \hline
% GNSS & - & - & - \\
% 10 & 2 & \SI{5.082}{\hertz} & \SI{102}{\second} \\
% 20 & 1 & \SI{10.164}{\hertz} & \SI{51}{\second} \\
% \hline
% \end{tabular}
% \end{center}
% \caption {DITL Test - FCORE configuration}
% \label{tab:ditl-cfg}
% \end{table}

@@

\begin{figure}[H]
\begin{tikzpicture}
\begin{axis} [
xlabel=Mission Elapsed Time (\SI{}{\second}),
ylabel=Received Data (\SI{}{\byte}),
mark size=1.0pt,
mark repeat={5},
legend style ={
    at={(0.02,0.95)}, 
    anchor=north west, draw=black, 
    fill=white,align=left
}
]

@@

\begin{table}[H]
\begin{center}
\begin{tabular}{ |c|c c c c| }
\hline
payload & up count & down count & recovering count & uprate \\
\hline
GNSS       & 67 & 0 & 2 & 97.1\% \\
payload 10 & 64 & 0 & 5 & 92.8\% \\
payload 20 & 63 & 0 & 6 & 91.3\% \\
\hline 
\end{tabular}
\end{center}
\caption {DITL Test - Platform health data}
\label{tab:ditl-health}
\end{table}

\subsection{Radio Stress-Testing}

@@

\begin{figure}[H]
\begin{tikzpicture}
\begin{axis} [
xlabel=Mission Elapsed Time (\SI{}{\second}),
ylabel=Received Data (\SI{}{\byte}),
mark size=1.0pt,
legend style ={
    at={(0.02,0.95)}, 
    anchor=north west, draw=black, 
    fill=white,align=left
}
]
\addplot+ table [
x=MET, y=received, col sep=comma
] {data/test-rs8.256/fcore.log.rxstats.csv};

@@

\begin{figure}[H]
\begin{tikzpicture}
\begin{axis} [
xlabel=Mission Elapsed Time (\SI{}{\second}),
ylabel=Received Data (\SI{}{\byte}),
mark size=1.0pt,
legend style ={
    at={(0.02,0.95)}, 
    anchor=north west, draw=black, 
    fill=white,align=left
}
]
\addplot+ table [
x=MET, y=received, col sep=comma
] {data/test-rs14.256/fcore.log.rxstats.csv};

@@

\begin{figure}[H]
\begin{tikzpicture}
\begin{axis} [
xlabel=Mission Elapsed Time (\SI{}{\second}),
ylabel=Received Data (\SI{}{\byte}),
mark size=1.0pt,
legend style ={
    at={(0.02,0.95)}, 
    anchor=north west, draw=black, 
    fill=white,align=left
}
]
\addplot+ table [
x=MET, y=received, col sep=comma
] {data/test-rs18.256/fcore.log.rxstats.csv};

@@

\begin{figure}[H]
\begin{tikzpicture}
\begin{axis} [
xlabel=Mission Elapsed Time (\SI{}{\second}),
ylabel=Error-Corrected Data (\SI{}{\byte}),
mark size=1.0pt,
legend style ={
    at={(0.02,0.95)}, 
    anchor=north west, draw=black, 
    fill=white,align=left
}
]

@@

\begin{table}[H]
\begin{center}
\begin{tabular}{ |c|c c| }
\hline
test & Correction Rate & Theoretical Error Rate \\
\hline
$\frac{8}{256}$  & \SI{2.826}{\percent} & \SI{3.125}{\percent} \\ [0.2em]
$\frac{14}{256}$ & \SI{3.655}{\percent} & \SI{5.469}{\percent} \\ [0.2em]
$\frac{18}{256}$ & \SI{2.514}{\percent} & \SI{7.031}{\percent} \\ [0.2em]
\hline 
\end{tabular}
\end{center}
\caption {DITL Test - Platform health data}
\label{tab:stress-fec}
\end{table}

>>>>

The following section presents the results of the tests done as part of the
evaluation process of the project, as discussed in section \ref{sec:testing}.

% \section{Component Testing}
%
% \section{Integrated Testing}

\section{Day In The Life Testing}
\label{ssec:results-ditl}

@@

\begin{figure}[h]
\begin{tikzpicture}
\begin{axis} [
xlabel=Mission Elapsed Time (\SI{}{\second}),
ylabel=Altitude (\SI{}{\metre}),
mark size=1.0pt,
mark repeat={5},
legend style ={
    at={(0.98,0.95)}, 
    anchor=north east, draw=black, 
    fill=white,align=left
}
]
\addplot+ table [
x=MET, y=altitude, col sep=comma
] {data/test-ditl/loc.csv};
\end{axis}
\end{tikzpicture}
\centering
\caption{DITL Test - Altitude over time}
\label{fig:dit-alt}
\end{figure}

The mission platform was composed of the AHABus \acrlong{obc}, and two simulated
payloads: payload 10 at priority level 2, and payload 20 at priority level 1.
Table \ref{tab:ditl-cfg} shows the core frequency and polling intervals for
each payload, generated from the mission file by the FCORE configuration tool.

\begin{table}[h]
\begin{center}
\begin{tabular}{c||c c c}

payload & priority & core frequency & polling interval \\ \hline
10 & 2 & \SI{5.082}{\hertz} & \SI{102}{\second} \\
20 & 1 & \SI{10.164}{\hertz} & \SI{51}{\second} \\

\end{tabular}
\end{center}
\caption {DITL Test - FCORE configuration}
\label{tab:ditl-cfg}
\end{table}

@@

\begin{figure}[h]
\begin{tikzpicture}
\begin{axis} [
xlabel=Mission Elapsed Time (\SI{}{\second}),
ylabel=Received Data (\SI{}{\byte}),
mark size=1.0pt,
mark repeat={5},
legend style ={
    at={(0.02,0.95)}, 
    anchor=north west, draw=black, 
    fill=white,align=left
}
]

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{c||c c c|c}

payload & up count & down count & recovering count & uptime ratio \\ \hline
GNSS       & 67 & 0 & 2 & 97.1\% \\
payload 10 & 64 & 0 & 5 & \SI{92.8}{\percent} \\
payload 20 & 63 & 0 & 6 & \SI{91.3}{\percent} \\

\end{tabular}
\end{center}
\caption {DITL Test - Platform health data}
\label{tab:ditl-health}
\end{table}

The number of valid and invalid packets received for each payload are given in
table \ref{tab:ditl-packet-count}, along with the expected number of packets
calculated from the FCORE configuration polling intervals given in table
\ref{tab:ditl-cfg} and the mission duration of \SI{8482}{\second}. The ratio of
received packets to expected packets matches the uptime ratios reported by
FCORE health packets, given in table \ref{tab:ditl-health}.

\begin{table}[h]
\begin{center}
\begin{tabular}{c||c c|c c|c}

payload & valid packets & invalid packets & total & expected & ratio \\
\hline
payload 10 & 71 & 2 & 79 & 83 & \SI{95.2}{\percent} \\
payload 20 & 138 & 6 & 144 & 166 & \SI{86.7}{\percent} \\

\end{tabular}
\end{center}
\caption {DITL Test - Received packets}
\label{tab:ditl-health}
\end{table}

\section{Radio System Resilience Testing}
\label{ssec:results-resilience}

@@

\begin{figure}[h]
\begin{tikzpicture}
\begin{axis} [
xlabel=Mission Elapsed Time (\SI{}{\second}),
ylabel=Received Data (\SI{}{\byte}),
mark size=1.0pt,
legend style ={
    at={(0.02,0.95)}, 
    anchor=north west, draw=black, 
    fill=white,align=left
}
]
\addplot+ table [
x=MET, y=received, col sep=comma
] {data/test-rs8.256/fcore.log.rxstats.csv};

@@

\begin{figure}[h]
\begin{tikzpicture}
\begin{axis} [
xlabel=Mission Elapsed Time (\SI{}{\second}),
ylabel=Received Data (\SI{}{\byte}),
mark size=1.0pt,
legend style ={
    at={(0.02,0.95)}, 
    anchor=north west, draw=black, 
    fill=white,align=left
}
]
\addplot+ table [
x=MET, y=received, col sep=comma
] {data/test-rs14.256/fcore.log.rxstats.csv};

@@

\begin{figure}[h]
\begin{tikzpicture}
\begin{axis} [
xlabel=Mission Elapsed Time (\SI{}{\second}),
ylabel=Received Data (\SI{}{\byte}),
mark size=1.0pt,
legend style ={
    at={(0.02,0.95)}, 
    anchor=north west, draw=black, 
    fill=white,align=left
}
]
\addplot+ table [
x=MET, y=received, col sep=comma
] {data/test-rs18.256/fcore.log.rxstats.csv};

@@

\begin{figure}[h]
\begin{tikzpicture}
\begin{axis} [
xlabel=Mission Elapsed Time (\SI{}{\second}),
ylabel=Error-Corrected Data (\SI{}{\byte}),
mark size=1.0pt,
legend style ={
    at={(0.02,0.95)}, 
    anchor=north west, draw=black, 
    fill=white,align=left
}
]

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{c||c c}

test & Correction Rate & Theoretical Error Rate \\ \hline
$\frac{8}{256}$  & \SI{2.826}{\percent} & \SI{3.125}{\percent} \\ [0.2em]
$\frac{14}{256}$ & \SI{3.655}{\percent} & \SI{5.469}{\percent} \\ [0.2em]
$\frac{18}{256}$ & \SI{2.514}{\percent} & \SI{7.031}{\percent} \\ [0.2em]

\end{tabular}
\end{center}
\caption {DITL Test - Platform health data}
\label{tab:stress-fec}
\end{table}
